\documentclass[12pt,a4paper]{report}

% Packages
\usepackage{geometry} % Adjust margins
\geometry{margin=1in}
\usepackage{graphicx} % For including images
\usepackage{amsmath}  % For mathematical equations
\usepackage{amssymb}  % For additional symbols
\usepackage{hyperref} % For hyperlinks
\usepackage{fancyhdr} % For custom headers and footers
\usepackage{setspace} % For line spacing
\usepackage{natbib}   % For citations and bibliography
\usepackage{titlesec} % For section formatting

% Custom header and footer
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\textit{Your Name}} % Left header
\fancyhead[R]{\textit{Report Title}} % Right header
\fancyfoot[C]{\thepage} % Center footer

% Title section formatting
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}
\titleformat{\subsection}{\normalsize\bfseries}{\thesubsection}{1em}{}

% Document starts
\begin{document}

% Title Page
\begin{titlepage}
    \centering
    \vspace*{1in}
    {\huge\bfseries Report Title \par}
    \vspace{1.5in}
    {\Large Your Name \par}
    \vfill
    {\large \today \par}
\end{titlepage}

% Abstract
\begin{abstract}
\noindent
This is a brief summary of your report. It should concisely describe the purpose of the report, the main findings or conclusions, and any recommendations. The abstract is typically around 150-250 words.\cite{exampleCitation}
\end{abstract}

% Table of Contents
\tableofcontents
\newpage

% Introduction
\chapter{Introduction}
\noindent
This is where you introduce the topic of your report. Provide background information, state the purpose of the report, and outline the structure of the document.

% Main Content Sections
\chapter{Main Section 1}
\noindent
This section should cover the first major topic of your report. Use subsections as needed.

\section{Subsection 1.1}
\noindent
Detail specific aspects of the topic here. You can include equations, figures, and tables as needed.

\subsection{Subsection 1.1.1}
\noindent
Further breakdown of topics can go here.

% Additional Sections
\chapter{Main Section 2}
\noindent
This section covers another major aspect of your report. Continue using subsections to organize your content.

% Conclusion
\chapter{Conclusion}
\noindent
Summarize the main points of your report, discuss any findings or conclusions, and propose any recommendations or future work.

% References
\newpage
\bibliographystyle{plainnat} % Or another style of your choice
\bibliography{references} % This assumes you have a .bib file with your references

\end{document}
